Spin canonical divisors of log stacky curves

### 2015-06-25 stacky_write_up/spin_cring.tex
minor intro edit

Following Voight and Zureick-Brown \cite{vzb:stacky}, we examine a
much more general setting, generalizing Petri's theorem in many
directions. A divisor $\Delta \in d X$ is a {\bf log divisor} if
$\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let
$(\sx,\Delta)$ denote a tame separably rooted curve over a
field $k$ so that $X$ is the coarse space of $\sx$, as defined in
\cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i
= 1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_
\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$,
be a divisor $\halfcan \in \di \sx$ so that $2\halfcan \sim K_\sx +
\Delta.$ If $X$ has genus $g$ and $\delta = \deg \Delta,$ then we
say $\sx$ has \textbf{signature} $(g; e_1, \ldots, e_r;\delta)$. A
{\bf log spin curve} is a triple $(X,\Delta,\halfcan)$ where $(X,\Delta)$
and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
The central object of study in this paper is the {\bf log spin
canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
\end{align*}

@@

\subsection{Definitions}
We reserve the notation $\halfcan$ for the halfcanonical divisor
where $\halfcan \sim $.

>>>>

Following Voight and Zureick-Brown \cite{vzb:stacky}, we examine a
much more general setting, generalizing Petri's theorem in many
directions. A divisor $\Delta \in d X$ is a {\bf log divisor} if
$\Delta = \sum_{i}^{}P_i \in \di X,$ with all $P_i$ distinct. Let
$(\sx,\Delta)$ denote a tame separably rooted curve over a
field $k$ so that $X$ is the coarse space of $\sx$, as defined in
\cite[Section 5.2]{vzb:stacky} so that $\di \sx = \di X \bigoplus_{i
= 1}^r \langle \frac{1}{e_i}P_i \rangle,$ with $e_i \in \BZ$. Let $K_
\sx = K_X + \sum_{i = 1}^{r}\frac{e_i - 1}{e_i}P_i.$ In this case, we
say $\sx$ has {\bf stabilizer order} $e_i$ at $P_i$. Call $\halfcan
\in \di \sx$ a {\bf log half-canonical divisor} on $(\sx,\Delta)$ if
$2\halfcan \sim K_\sx + \Delta$. If $X$ has genus $g$ and $\delta := \deg \Delta,$ then we
say $\sx$ has \textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$. A
{\bf log spin curve} is a triple $(X, \Delta, \halfcan)$ where $(X,\Delta)$
and $\halfcan$ is a log half-canonical divisor on $(\sx,\Delta)$.
The central object of study in this paper is the {\bf log spin
canonical ring} of $(X,\Delta,L)$ is
\begin{align*}
	R(X,\Delta,L) = \bigoplus_{n \geq 0} H^0(X,nL)
\end{align*}

@@

\subsection{Definitions}
We reserve the notation $\halfcan$ for the halfcanonical divisor
where $2\halfcan \sim K_\sx + \Delta$.
